---
title: "EDA Assignment Prep"
author: "Amber Camp"
format: html
editor: visual
---

## EDA Assignment Prep: Pokemon data

### Libraries

```{r}
library(here)
library(tidyverse)
library(janitor)
```

### Data

```{r}
pokedata <- read_csv(here("data/Pokemon.csv"))

pokedata <- pokedata %>%
  clean_names()
```

### Describe the data:

Data author:

Description:

How many observations (rows) are there?

How many variables (columns) are there?

### skimr: Quick overview

```{r}
skim_data <- skimr::skim(pokedata)
```

### Summary: Quick overview

```{r}
summary(pokedata)
```

### Categorical vs. Continuous

```{r}
class(pokedata$number)
pokedata$number <- as.factor(pokedata$number)
class(pokedata$number)
summary(pokedata$number)

summary(pokedata$type_1)
pokedata$type_1 <- as.factor(pokedata$type_1)
class(pokedata$type_1)
summary(pokedata$type_1)
```

How many categorical variables are there? 5, (6)

How many continuous variables are there? 7

What are some variables of interest to you?

------------------------------------------------------------------------

## EDA Assignment Prep: \[Insert Data Name Here\]

### Libraries

```{r}
library(here)
library(tidyverse)
library(janitor)
```

### Data

```{r}
mets_pitching <- read_csv(here("data/NYM_pitching.csv"))

mets_pitching <- mets_pitching %>%
  clean_names()
```

### Describe the data:

Data author: Matt OP

Description: New York Mets pitching data from 1962 - 2023

How many observations (rows) are there? 1,296

How many variables (columns) are there? 37

### Summary: Quick overview

```{r}
summary(mets_pitching)
```

### Categorical vs. Continuous

```{r}

```

How many categorical variables are there? 7

How many continuous variables are there? 30

What are some variables of interest to you? ranked, ERA, innings pitched, walks, strikeouts, strikeout to walk ratio

What kinds of questions could you explore with this data? In a given year who was the #1 ranked pitcher and what was there ERA, IP, BB, K, K/BB.
