---
title: "Homework 8: Class Wrap-up"
format: html
editor: visual
---

## Homework 8: Class Wrap-up

We are finally at the end of the semester! The final homework for the class will be to summarize and share some of the things we've done so far.

The plan is for everyone to be randomly paired with a tiny topic pertaining to something we've learned together this semester and then submit a code snippet to be presented in class on Wednesday, 11/20.

#### Libraries

```{r, message=FALSE}
library(tidyverse)
library(here)
```

#### Read in the list of topics

```{r, message=FALSE}
topics <- read_csv("cs201_topics.csv")
view(topics)

# anything to edit?
#topics[#, "topic"] <- 
```

#### Read in the list of student names

```{r, message=FALSE}
names <- read_csv("cs201_names.csv")
view(names)
```

#### Generate a random number in the names dataframe

```{r, message=FALSE}
names <- names %>%
  mutate(number = sample(1:8, nrow(names), replace = FALSE))

view(names)
```

#### Join the names to the topics

```{r, message=FALSE}
assigned_topics <- names %>%
  full_join(topics, by = "number")

view(assigned_topics)
```

### Instructions

1.  Find your assigned topic. Talk to me if you reeeeeeaaaally want to do something else, or trade with someone (but let me know).

2.  Prepare a code snippet that briefly (2-3 mins) explains the topic in the code chunk below, using `penguins` data.

3.  Push to GitHub BY NOON on Wednesday 11/20 (I'll need time to download and compile before class).

4.  Come to class next Wednesday and show us how it's done :)

#### Extra libraries needed (if any)

```{r, message=FALSE}
library(janitor)

```

#### Read in penguins data

```{r, message=FALSE}
penguins <- read_csv(here("data/penguins_lter.csv"))

penguins <- penguins %>% 
  clean_names()
```

#### {Insert topic here}

```{r, message=FALSE}
penguins_hw_8 <- penguins %>%
  mutate(
    size_of_penguin = case_when(
      body_mass_g < 3000 ~ "Small Penguin", 
      # If body mass < 3000g, then call it Small
      body_mass_g >= 3000 & body_mass_g <= 4000 ~ "Medium Penguin", 
      # If between 3000g and 4000g, then call it Medium
      body_mass_g > 4000 ~ "Large Penguin",     
      # If > 4000g, then call it Large
      TRUE ~ "Unknown Size"                  
      # If it is anything else call it unknown; because there is no weight
      
    )) %>%
  select(species, island, body_mass_g, size_of_penguin)
#select to only show these columns

# Show penguins_hw_8
show(penguins_hw_8)

```
